Differentially Private Bayesian Inference

### 2018-04-02 main.tex
update title
update dilation expomech
update format
update

\title{\textbf{Notes of DP - Bayesian Inference}\\}
\author{Jiawen \textsc{Liu}}

\begin{document}
\section{Setting up}
\label{sec_setup}
The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$. For conciseness, when prior is given, we use $\bysinfer(x)$.

@@

\begin{small}
\begin{equation*}
\begin{split}
& \sqrt{
1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + m + \frac{n}{2} + 1 + m + 1}{2},
\frac{\frac{n}{2} + 1 - m + \frac{n}{2} + 1 - m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
}
}
}\\
& < \sqrt{
1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + m + 1 + \frac{n}{2} + 1 + m + 2}{2},
\frac{\frac{n}{2} + 1 - m - 1 + \frac{n}{2} + 1 - m - 2}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}
}\\
\\
& \frac{\betafun(\frac{n + 2m + 3}{2}, \frac{n - 2m + 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
}
}\\
& > \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}
\end{split}
\end{equation*}
\end{small}

@@

\begin{small}
\begin{equation*}
\begin{split}
& \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})
\frac{n - 2m - 1}{n + 2m + 3}}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
\frac{n - 2m}{n + 2m + 2}
}
}\\
> & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})
\frac{n - 2m - 3}{n + 2m + 5}}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
\frac{n - 2m - 2}{n + 2m + 6}
}
}\\
\end{split}
\end{equation*}

\begin{equation*}
\begin{split}
& \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
> & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
\\
& \sqrt{1 - \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
< & \sqrt{1 - \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
\\
& \hlg(beta(\frac{n}{2} + 2 + m, \frac{n}{2} - m), beta(\frac{n}{2} + 3 + m, \frac{n}{2} - 1 - m))\\
< & \hlg(beta(\frac{n}{2} + m + 3, \frac{n}{2} - 1 - m), beta(\frac{n}{2} + m + 4, \frac{n}{2} - m - 2))\\
\end{split}
\end{equation*}
\end{small}

@@

\begin{equation*}
\begin{split}
\because \footnote{the symbol of $\because$ here means because}
\quad 		& \Delta_l u(x) = |\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|,\\
					& \max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}};\\
\because \quad 		& \hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)\\
					& \leq \hlg(\bysinfer(x), \bysinfer(y'));\\
\therefore \footnote{the symbol of $\therefore$ here means therefore}
\quad 	& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(y')),\\
					& \max_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}};\\
\therefore \quad 	& \Delta_l u(x) = \max \{\hlg(\bysinfer(x), \bysinfer(x + 1)),\\
					& \quad \quad \quad \quad \quad \quad \quad \hlg(\bysinfer(x), \bysinfer(x - 1))\};\\
					& According\ to\ Statement\ I:\\
\mathsf{if}	  \quad	& x > x_0 \\
\mathsf{then} \quad	
					& \hlg(\bysinfer(x), \bysinfer(x - 1))\\
					&< \hlg(\bysinfer(x), \bysinfer(x + 1));\\
\mathsf{then} \quad	
					& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(x + 1));\\
\mathsf{if}	 \quad	& x < x_0 \\
\mathsf{then} \quad	
					& \hlg(\bysinfer(x), \bysinfer(x - 1))\\
					& > \hlg(\bysinfer(x), \bysinfer(x + 1)); \\
\mathsf{then} \quad	
					& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(x - 1));\\
\mathsf{else} \quad	
					& \Delta_l u(x_0) = \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1))\\
					& \quad \quad \quad = \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1)). \\
\end{split}
\end{equation*}

@@

\subsubsection{Statement III}
\begin{proof}
From Statement I and Statement II, we can conclude that:
\begin{equation*}
\begin{split}
\mathsf{when} \quad	& x > x_0 \\
					& \hlg(\bysinfer(x), \bysinfer(x + 1) \\
					& > \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1); \\
					& i.e.\ \Delta_l u(x) > \Delta_l u(x_0)\\
\mathsf{when} \quad	& x < x_0 \\
					& \hlg(\bysinfer(x), \bysinfer(x - 1) \\
					& > \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1); \\
					& i.e.\ \Delta_l u(x) > \Delta_l u(x_0).\\
\end{split}
\end{equation*}

@@

\subsection{Dilation Property of Exponential Mechanism}

>>>>

\title{\textbf{Notes of DP - Bayesian Inference}\\}
% \author{Jiawen \textsc{Liu}}
\date{\vspace{-10ex}}

\begin{document}
\maketitle

\section{Setting up}
\label{sec_setup}
The Bayesian inference process is denoted as $\bysinfer(x,prior)$ taking an observed data set $x \in \mathcal{X}^n$ and a prior distribution as input, outputting a posterior distribution $posterior$. For conciseness, when prior is given, we use $\bysinfer(x)$.

@@

\begin{small}
\begin{equation*}
\begin{split}
\sqrt{
1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + m + \frac{n}{2} + 1 + m + 1}{2},
\frac{\frac{n}{2} + 1 - m + \frac{n}{2} + 1 - m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
}
}
}
& < \sqrt{
1 - \frac{\betafun(
\frac{\frac{n}{2} + 1 + m + 1 + \frac{n}{2} + 1 + m + 2}{2},
\frac{\frac{n}{2} + 1 - m - 1 + \frac{n}{2} + 1 - m - 2}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}
}\\
\\
\frac{\betafun(\frac{n + 2m + 3}{2}, \frac{n - 2m + 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 1 + m, \frac{n}{2} + 1 - m)
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
}
}
& > \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}
\end{split}
\end{equation*}
\end{small}

@@

\begin{small}
\begin{equation*}
\begin{split}
 \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})
\frac{n - 2m - 1}{n + 2m + 3}}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
\frac{n - 2m}{n + 2m + 2}
}
}
> & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})
\frac{n - 2m - 3}{n + 2m + 5}}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
\frac{n - 2m - 2}{n + 2m + 6}
}
}\\
\end{split}
\end{equation*}

\begin{equation*}
\begin{split}
\frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}
> & \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}\\
\\
\sqrt{1 - \frac{\betafun(\frac{n + 2m + 5}{2}, \frac{n - 2m - 1}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}
< & \sqrt{1 - \frac{\betafun(\frac{n + 2m + 7}{2}, \frac{n - 2m - 3}{2})}
{\sqrt{
\betafun(\frac{n}{2} + 2 + m, \frac{n}{2} - m)
\betafun(\frac{n}{2} + 3 + m, \frac{n}{2} - m - 1)
}
}}\\
\\
\hlg(beta(\frac{n}{2} + 2 + m, \frac{n}{2} - m), beta(\frac{n}{2} + 3 + m, \frac{n}{2} - 1 - m))
< & \hlg(beta(\frac{n}{2} + m + 3, \frac{n}{2} - 1 - m), beta(\frac{n}{2} + m + 4, \frac{n}{2} - m - 2))\\
\end{split}
\end{equation*}
\end{small}

@@

\begin{equation*}
\begin{split}
\because \footnote{the symbol of $\because$ here means because}
\quad 		& \Delta_l u(x) = \max_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\max_{\{r\in R\}} |\hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r)|,\\
\because \quad 		& \hlg(\bysinfer(x), r) - \hlg(\bysinfer(y'), r) \leq \hlg(\bysinfer(x), \bysinfer(y'));\\
\therefore \footnote{the symbol of $\therefore$ here means therefore}
\quad 	& \Delta_l u(x) = \max_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}} \hlg(\bysinfer(x), \bysinfer(y')),\\
\therefore \quad 	& \Delta_l u(x) = \max \{\hlg(\bysinfer(x), \bysinfer(x + 1)), \hlg(\bysinfer(x), \bysinfer(x - 1))\};\\
					& According\ to\ Statement\ I:\\
\mathsf{if}	  \quad	& x > x_0 \\
\mathsf{then} \quad	
					& \hlg(\bysinfer(x), \bysinfer(x - 1)) < \hlg(\bysinfer(x), \bysinfer(x + 1));\\
\mathsf{then} \quad	
					& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(x + 1));\\
\mathsf{if}	 \quad	& x < x_0 \\
\mathsf{then} \quad	
					& \hlg(\bysinfer(x), \bysinfer(x - 1))  > \hlg(\bysinfer(x), \bysinfer(x + 1)); \\
\mathsf{then} \quad	
					& \Delta_l u(x) = \hlg(\bysinfer(x), \bysinfer(x - 1));\\
\mathsf{else} \quad	
					& \Delta_l u(x_0) = \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1)) = \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1)). \\
\end{split}
\end{equation*}

@@

\subsubsection{Statement III}
\begin{proof}
From Statement I and Statement II, we can conclude that:
\begin{equation*}
\begin{split}
\mathsf{when} \quad	& x > x_0 \\
					& \hlg(\bysinfer(x), \bysinfer(x + 1) > \hlg(\bysinfer(x_0), \bysinfer(x_0 + 1); \\
					& i.e.\ \Delta_l u(x) > \Delta_l u(x_0)\\
\mathsf{when} \quad	& x < x_0 \\
					& \hlg(\bysinfer(x), \bysinfer(x - 1)  > \hlg(\bysinfer(x_0), \bysinfer(x_0 - 1); \\
					& i.e.\ \Delta_l u(x) > \Delta_l u(x_0).\\
\end{split}
\end{equation*}

@@

\subsection{Dilation Property of Exponential Mechanism}
\begin{lem}
for any exponential mechanism $\expomech$, $\lambda = f(\epsilon, \delta)$, $\epsilon$ and $|\delta| < 1$, the dilation property holds:

\begin{equation*}
\underset{z \thicksim \expomech}{Pr}[u(r,x) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \expomech}{Pr}[u(r,x) = e^{\lambda} \hat{s}] + \frac{\delta}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.
\end{lem}

\begin{equation*}
\begin{split}
\frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL_x}
& \leq \frac{exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)})}{NL_x}\\
exp(\frac{\epsilon \hat{s}}{2 S(x)})
& \leq exp(\frac{\epsilon (\hat{s} \cdot e^{\lambda})}{2 S(x)}) \\
\frac{\epsilon \hat{s}}{2 S(x)}
& \leq \frac{\epsilon}{2} + \frac{\epsilon \hat{s} \cdot  e^{\lambda}}{2 S(x)}\\
\hat{s} & \leq S(x) + \hat{s} \cdot e^{\lambda}\\
(1 - e^{\lambda}) \cdot \hat{s} & \leq S(x)
\end{split}
\end{equation*}

To proof this, we discuss some cases:
\begin{itemize}
	\item $\lambda > 0$
	\begin{itemize}
		\item $u(x,r) > 0$
		\item $u(x,r) < 0$
	\end{itemize}
	\item $\lambda < 0$
	\begin{itemize}
		\item $u(x,r) > 0$
		\item $u(x,r) < 0$
	\end{itemize}
\end{itemize}
